article title

### 2022-07-25 pilon_gilles_glossary.tex
Update statistical control
Add Nelson's Rules

@@

    description={A process is said to be in a state of statistical control if the variation for both charts is stable and predictable. This means that no points fail various control chart rules and no systematic patterns of variation are present.}

>>>>

\newglossaryentry{nelsons_rules}
    name={Nelson's Rules},
    description={They are a set of process behaviour chart rules for assessing statistical control.}

@@

    description={A process is said to be in a state of statistical control if the variation for both charts is stable and predictable. This means that no points fail various control chart rules, such as Nelson's rules, and no systematic patterns of variation are present. It is also called process stability.}
